SDR enhancement by clouds

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 19:27

<!-- ```{r echo=FALSE, fig.cap="Distribution of CE above reference"} -->
<!-- knitr::include_graphics("../images/relative_distributions-2.png") -->
<!-- ``` -->

```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
knitr::include_graphics("../images/relative_distributions-4.png")
```

>>>>

<!-- ```{r echo=FALSE, fig.cap="Distribution of CE above reference"} -->
<!-- knitr::include_graphics("../images/relative_distributions-2.png") -->
<!-- ``` -->
<!--
```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
knitr::include_graphics("../images/relative_distributions-4.png")
```
-->

```{r echo=FALSE, fig.cap="Distribution of CE over irradiance"}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```
